Ternary plots for `hyper2` samples

### 2024-10-18 inst/ternaryplot_hyper2.Rmd
consistentification

---
title: "Ternary plots for hyper2 samples"
author: "Robin Hankin"
output: html_document
bibliography: hyper2.bib  # copy vignettes/hyper2.bib to inst/
---

@@

@@

```{r loadlibraries}
library("hyper2")
library("Ternary")
```

>>>>

---
title: "Ternary plots for `hyper2` samples"
author: "Robin Hankin"
output: html_document
bibliography: hyper2.bib  # copy vignettes/hyper2.bib to inst/
---

@@

(takes about fifteen minutes to run without cache).

@@

```{r loadlibraries}
suppressPackageStartupMessages(library("Ternary"))
suppressPackageStartupMessages(library("hyper2"))
```
